Foregrounds in Fourier Space for Redshifted 21~cm Observatories

### 2015-02-06 ms.tex
Complete Introduction section
from 23a1bee:
============

In ms.tex,

(*) Complete Introduction section

After matching observations from the Murchison Widefield Array with instrumental simulations of the entire sky, we examine the {\bf shape of the delay spectrum} of each baseline. We report two important findings: the foregrounds that most severely {\bf obscure} the redshifted 21~cm power spectrum are not caused by emission in the central field of view, but rather by bright objects from near the horizon; and, diffuse Galactic emission plays a significant role hitherto unpredicted. We quantify these by separating the simulations into components based on type of foreground emission. We then arrive at a new method for minimizing the contribution of bright foregrounds which uses prior knowledge of the sky to down--weight adversely contaminated baselines. {\bf We also examine the role of antenna shapes in determining foreground contamination and provide inputs on antenna design for future EoR experiments}.

In \S\ref{sec:delay-spectrum} we {\bf provide a brief overview of the delay spectrum technique} \citep{par12a,par12b}. In \S\ref{sec:data}, we describe the MWA setup, summarize the observing parameters, and present the resulting data. Simulations using these observing parameters are described in \S\ref{sec:modeling} and analyzed by sky location and type of emission in \S\ref{sec:delay-spectrum-analysis}. In \S\ref{sec:fg-grading}, we offer an initial description of a more precise foreground avoidance technique. {\bf The role of antenna shapes in determining foreground contamination is explored in \S\ref{sec:antenna-shape}}. We present a summary of our work and findings in \S\ref{sec:summary}.

@@

\section{MWA Data Modeling}\label{sec:data}

>>>>

{\bf We investigate signatures generic to all wide--field measurements of EoR power spectrum and explore antenna shapes that are most desirable from the viewpoint of foreground contamination for future EoR experiments}. After matching observations from the Murchison Widefield Array with instrumental simulations of the entire sky, we examine the {\bf shape of the delay spectrum} of each baseline. We report two important findings: the foregrounds that most severely {\bf obscure} the redshifted 21~cm power spectrum are not caused by emission in the central field of view, but rather by bright objects from near the horizon; and, diffuse Galactic emission plays a significant role hitherto unpredicted. We quantify these by separating the simulations into components based on type of foreground emission. We then arrive at a new method for minimizing the contribution of bright foregrounds which uses prior knowledge of the sky to down--weight adversely contaminated baselines.

In \S\ref{sec:delay-spectrum} we {\bf provide a brief overview of the delay spectrum technique} \citep{par12a,par12b}. We establish the signatures arising from the nature of wide--field measurements in \S\ref{sec:wide-field}. In \S\ref{sec:sim}, we present the foreground model and a variety of instrument models to rank antenna shapes based on the criterion of foreground contamination. In \S\ref{sec:MWA}, we describe the MWA setup, summarize the observing parameters, and present the resulting data. Simulations using these observing parameters are compared with the data and analyzed for foreground signatures. In \S\ref{sec:fg-grading}, we offer an initial description of a more precise foreground avoidance technique. We present a summary of our work and findings in \S\ref{sec:summary}.

@@

\section{MWA Data Modeling}\label{sec:MWA}
